An Overview of Distributed Version Control Systems

### 2010-07-04 laarsample.tex
Mejorado el punto Architecture.Distributed

%----------------------------------------------------------------------
% SECTION II: Architecture
%----------------------------------------------------------------------
\section{ARCHITECTURE}
\label{ARCHITECTURE}

% - Distributed / Architecture
% - push-pull-commit (local commit, distributed repositories)
% - Flexibility
% - Changesets & patches
% - Cherry-picking
% - Merging
% - Tagging & branching
% - Trust Based Security

% Descripcion de arquitectura 
A DVCS has many features that make it perfect for distributed and non-distributed developments.

Almost every feature is based on the fact that a DVCS is distributed instead of centralized.

Therefore if you work distributed then merges would happen on a regular basis and they should be as fast and easy as possible, providing developers with a whole new set of tools that relieve them almost completely from having to code according to the rules required to work with a centralized CVS like system. 
%Arq
\subsection{Distributed}
The idea behind a distributed architecture means that no server has the full content of a repository. Instead of that, each 
particular developer has a clone of the repository with the changes he has commited. 
This allows users to version their changes in their own repository's clone while working in a offline environment.

As explained in section \sectionReference{CENTRALIZED DISTRIBUTED COMPARISON}  \sectionReference{Commits} all commits are local which makes the whole versioning system faster.

% Local commit

>>>>

%----------------------------------------------------------------------
% SECTION II: Architecture
1%----------------------------------------------------------------------
\section{ARCHITECTURE}
\label{ARCHITECTURE}

\subsection{Distributed}
The idea behind a distributed architecture means that no server has the full content of a repository. Instead of that, each 
particular developer has a clone of the repository with the changes he has commited. 
This allows users to version their changes in their own repository's clone while working in a offline environment. This means that the developer's commit
will, at first, remain on its local clone where no one else can see them. This makes the whole versioning system faster and is explained in section \sectionReference{CENTRALIZED DISTRIBUTED COMPARISON}  \sectionReference{Commits}

Then the developers can share their changes by pushing them into someone else's repository or by pulling changes from them.
Therefore, if you work distributed, merges would happen on a regular basis and they should be as fast and easy as possible, providing developers with a whole new set of tools that relieve them almost completely from having to code according to the rules required to work with a centralized CVS like system.
